Signed Peripherality Functions for Multivariate Statistical Inference

### 2018-04-01 MS-new/3_Scale.tex
.

Condition (A2) in Section~\ref{section:LocSection} is now replaced by the stronger condition (B2). Note that all the current conditions are essentially the opposite of those imposed on a traditional depth function \citep{zuo00}. Given a depth function, the peripherality functions in this section can be defined as a bounded monotonically decreasing function of it. Consequently, we use the term {\it inverse depth function} in place of peripherality functions in this section, denoting them by $D^-(\bfx,\BF)$, or equivalently $D^-_\bfX(\bfx)$.

Given an inverse depth function $D^-_{\bfX}(\bfx)$ we transform the original random variable as: $\tilde \bfX = D^-_\bfX(\bfx) \bfS(\bfx - \bfmu)$. We use the transformed data matrix $\tilde \BX = (\tilde \bfx_1, \ldots, \tilde \bfx_n)^T$ as proxy of the original data matrix $\BX$ for improved estimation of the components of the population covariance matrix $\Sigma$ in this section. To this end, in Section~\ref{subsec:dcm} we give some results characterizing the population covariance matrix of these vectors, i.e. $\BV \tilde \bfX$, and its affine equivariant counterpart. Section~\ref{subsec:dcm} gives asymptotic properties of their finite sample versions. In Section~\ref{subsec:robustPCA}, we use eigenvectors of these estimates for robust PCA, deriving their influence functions, as well as asymptotic and finite sample efficiencies. Finally in Section~\ref{subsec:plugin}, we calculate robust estimates of eigenvalues and propose a plug-in robust estimate of $\Sigma$.

@@

\begin{enumerate}
\item Start from some initial estimates $(\bfmu_{Dw}^{(0)}, \Sigma_{Dw}^{(0)}$. Set $t=0$;

@@

\item Update the location estimate:
%
$$
\bfmu_{Dw}^{(t+1)} = \frac{\sum_{i=1}^n \tilde \bfx_i / \| \bfz_i^{(t)} \| }{\sum_{i=1}^n 1 / \| \bfz_i^{(t)} \|};
$$
%
\item Update the scatter estimate:
%
$$
\Sigma_{Dw}^{*(t+1)} = \frac{1}{n} \sum_{i=1}^n \frac{(D^{n-}_\bfX (\bfx_i))^2 (\bfx_i - \bfmu_{Dw}^{(t+1)})(\bfx_i - \bfmu_{Dw}^{(t+1)})^T}{\| \bfz_i^{(t)} \|^2}; \quad \Sigma_{Dw}^{*(t+1)} \leftarrow \frac{\Sigma_{Dw}^{*(t+1)}}{\text{det} (\Sigma_{Dw}^{*(t+1)})^{1/p}}.
$$
%
\item Continue until convergence.
\end{enumerate}

>>>>

Condition (A2) in Section~\ref{section:LocSection} is now replaced by the stronger condition (B2). Note that all the current conditions are essentially the opposite of those imposed on a traditional depth function \citep{zuo00}. Given a depth function, the peripherality functions in this section can be defined as a bounded monotonically decreasing function of it. Consequently, we use the term {\it inverse depth function} \citep{MajumdarChatterjeeStat} in place of peripherality functions in this section, denoting them by $D^-(\bfx,\BF)$, or equivalently $D^-_\bfX(\bfx)$. For ease of exposition, we stick to the following inverse transformation: $D^-_\bfX(\bfx) = \sup_\bfy D^-_\bfX(\bfy) - D^-_\bfX(\bfx)$ from now on. The theoretical results go through with minor changes for other choices of inverse depths.

Given a choice of inverse depth function $D^-_{\bfX}(\bfx)$, we transform the original random variable as: $\tilde \bfX = D^-_\bfX(\bfx) \bfS(\bfx - \bfmu)$. We use the transformed data matrix $\tilde \BX = (\tilde \bfx_1, \ldots, \tilde \bfx_n)^T$ as proxy of the original data $\BX$ for improved estimation of the components of the population covariance matrix $\Sigma$ in this section. To this end, in Section~\ref{subsec:dcm} we give some results characterizing the population covariance matrix of these vectors, i.e. $\BV \tilde \bfX$, and its affine equivariant counterpart. Section~\ref{subsec:sample-DCM} gives asymptotic properties of their finite sample versions. In Section~\ref{subsec:robustPCA}, we use eigenvectors of these estimates for robust PCA, deriving their influence functions, as well as asymptotic and finite sample efficiencies. Finally in Section~\ref{subsec:plugin}, we calculate robust estimates of eigenvalues and propose a plug-in robust estimate of $\Sigma$.

@@

\begin{enumerate}
\item Start from some initial estimates $(\bfmu_{Dw}^{(0)}, \Sigma_{Dw}^{(0)})$. Set $t=0$;

@@

\item Update the location estimate:
%
$$
\bfmu_{Dw}^{(t+1)} = \frac{\sum_{i=1}^n \tilde \bfx_i / \| \bfz_i^{(t)} \| }{\sum_{i=1}^n \| \bfz_i^{(t)} \|^{-1} };
$$
%
\item Update the scatter estimate:
%
$$
\Sigma_{Dw}^{*(t+1)} = \frac{1}{n} \sum_{i=1}^n \frac{(D^{n-}_\bfX (\bfx_i))^2 (\bfx_i - \bfmu_{Dw}^{(t+1)})(\bfx_i - \bfmu_{Dw}^{(t+1)})^T}{\| \bfz_i^{(t)} \|^2}; \quad \Sigma_{Dw}^{*(t+1)} \leftarrow \frac{\Sigma_{Dw}^{*(t+1)}}{\text{det} (\Sigma_{Dw}^{*(t+1)})^{1/p}}.
$$
%
\item Continue until convergence.
\end{enumerate}
